
\section{IX \textendash{} Constitution}
Note:  This section should specify how the constitution is approved and amended,
and the specific process for introducing, voting on, and approving amendments
and by-laws.
\begin{enumerate}
  \item Adoption
    \begin{enumerate}
      \item Adoption of a new constitution shall be performed by the Executive
        Board. The new constitution must be drafted or sponsored by a member of
        the Executive Board. The draft must then be presented at an Executive
        meeting. The Board will be allowed to ask questions, suggest amendments,
        and discuss the new constitution. One week after the draft is presented,
        the Executive Board will meet for a formal vote of the new constitution.
        If quorum is not reached, the vote will be postponed until the next
        meeting where quorum is achieved. All executive board members present
        except 2 must approve the new constitution for it to take affect.
      \item	S\&T ACM’s constitution must have the approval of Student
        Organization Recognition Committee.
      \item	Final approval of S\&T ACM’s constitution must come from the Vice
        Chancellor of Student Affairs for this constitution to be valid and take
        full effect.
    \end{enumerate}
  \item	Amendments:
    \begin{enumerate}
      \item Any amendments to the constitution must be submitted as Pull
      Requests to the S\&T ACM constitution repository.
      \item Changes to the constitution must be formally presented to the
      Executive Board at least five days before any vote occurs. This will not
      include stylistic changes to formatting.
      \item The vote will take place in person and after discussion the vote
        will take place. Each person voting will have the choice of approval or
        denial. For the changes to be passed, the Board must get approval from
        greater than or equal to all members except two.
      \item	Approval of Student Organization Recognition Committee or its
        representative
      \item	Student Involvement will be notified of any amendments voted in, and
        provided with a copy of the changes made.
    \end{enumerate}
  \item	By-laws (If by-laws are called for in the constitution, they should
    contain information subject to frequent change.  The constitution should
    contain the information not required for frequent revision): Note:  The
    process for by-laws may be similar to the process for amendments.  You will
    want to include similar information regarding the by-law process as you did
    for the amendments.
    \begin{enumerate}
      \item	Changes to the by laws may be introduced as a pull request on the
        constitution repo.
      \item	A 2/3s majority vote of Executive Board members at an Executive
        Meeting with quorum is required to approve the by-law amendment.
      \item	Must be provided to the Department of Student Involvement upon
      approval.
    \end{enumerate}
\end{enumerate}
