
\section{IX - Rules and regulations}
Note:  This section should express that the organization will follow all federal
and state laws and abide by university policies.  If this organization is
affiliated with a national organization, they will also want to express that
they will abide by the policies of the national organization as well.  Lastly,
this section should include a statement on the organizations policy on hazing
and alcohol use.
\begin{enumerate}
\item (Organization) will follow federal and state laws and abide by the rules
of the university
\item (Organization) will follow the rules/regulations of national organization
(if applicable)
\item The Code of Conduct for (Organization) members is the University of
Missouri Code of Conduct and this constitution.
\item This organization is responsible for behaving in a manner compatible with
the university’s standard for student organizations and Title IX federal laws.
All forms of hazing, condoning and sanctioning of physical abuse, sexual
harassment and sexual violence towards prospective or current members are
illegal and will be immediately reported to the Office of Affirmative Action,
Diversity and Inclusion or to the Office of Community Standards and Student
Conduct for review and possible disciplinary action.
\item Alcohol Use – This organization is responsible for abiding by state law
and university policy for use of alcoholic beverages and controlled substances;
unless consumption is prohibited by the organization, guidelines for responsible
use will be set accordingly. {Guidelines may be listed here or in bylaws}. In
accordance with university policy, student organization funds administered
through a university account may not be used to purchase alcohol, alcohol will
not be publicized in promotional materials, and alcohol will not be consumed on
university property without an approved alcohol permit. Failure to comply with
the university’s alcohol policy will be immediately reported to the Office of
Community Standards and Student Conduct for review and possible disciplinary
action.
  \begin{enumerate}
    \item Note: The responsible and legal use of alcohol is not prohibited by
    the University. You may not use University funds to purchase alcohol, you
    may not have alcohol at sponsored events on University property without
    express permission by the Chancellor, you may not publicize alcohol at an
    event in your advertisements. All violations of the University alcohol
    policy and/or illegal use of alcohol MUST be reported to the Office of
    Community Standards. 
  \end{enumerate}
\end{enumerate}

