
\section{X \textendash{} Constitution}
Note:  This section should specify how the constitution is approved and amended,
and the specific process for introducing, voting on, and approving amendments
and by-laws.
\begin{enumerate}
  \item Adoption
    \begin{enumerate}
      \item Adoption of a new constitution shall be performed by the Executive
        Board. To affect a new constitution, the constitution may be drafted or
        sponsored by a member of the Executive Board. The draft must then be
        presented to the Executive Board at an Executive meeting. The members of
        the Executive board will be allowed to ask questions, suggest
        amendments, and discuss the new constitution. One week after the draft
        is presented, the Executive Board will meet for a formal vote of the new
        constitution in which 2/3s of the Executive Board is necessary for
        quorum. If quorum is not achieved, the vote will be postponed until the
        next meeting where quorum is achieved. All Executive Board members
        present except one must approve of the new constitution.
      \item	S\&T ACM’s constitution must have the approval of Student
      Organization Recognition Committee.
      \item	Final approval of S\&T ACM’s constitution must come from the
      Vice Chancellor of Student Affairs for this constitution to be valid and
      take full effect.
    \end{enumerate}
  \item	Amendments:
    \begin{enumerate}
      \item Any amendments to the constitution must be submitted as Pull
      Requests to the S\&T ACM constitution repository.
      \item Changes to the constitution must be formally presented to the
      Executive Board at least five days before any vote occurs. This will not
      include stylistic changes to formatting.
      \item The vote will take place in
      person and after discussion the vote will take place. Each person voting
      will have the choice of approval or denial. For the changes to be
      passed, the Board must get approval from greater than or equal to all
      members except two.
      \item	Approval of Student Organization Recognition Committee or its
      representative
      \item	Student Involvement will be notified of any amendments voted in, and
      provided with a copy of the changes made.
    \end{enumerate}
  \item	By-laws (If by-laws are called for in the constitution, they should
contain information subject to frequent change.  The constitution should contain
the information not required for frequent revision): Note:  The process for
by-laws may be similar to the process for amendments.  You will want to include
similar information regarding the by-law process as you did for the amendments.
    \begin{enumerate}
      \item	Clause reflecting a need for by-laws.
      \item	Vote needed for adoption
      \item	Vote needed for amending by-laws
      \item	When by-laws may be adopted or revised (special meeting, regular
      meeting, etc)
      \item	Must be provided to the Department of Student Involvement upon
      approval
    \end{enumerate}
\end{enumerate}
